### 2016-03-28 config/styles.inc.tex
Grid behind plots, axis+tick on top

\pgfplotsset{tick style={black!30},grid style={black!10}}
\pgfplotsset{every axis legend/.append style={font=\footnotesize}}
\pgfplotsset{every axis label/.append style={font=\footnotesize}}
\pgfplotsset{every tick label/.append style={font=\footnotesize}}
\pgfplotsset{every axis title/.append style={at={(0.5,1.025)}}}
\pgfplotsset{every axis post/.style={unbounded coords=jump, line join=round}}

@@

\pgfplotsset{frf/.style={color=black,solid,line width=1pt}}
\pgfplotsset{bw/.style={fill=bwfill,draw=bwline,area legend}}
\pgfplotsset{signal/.style={ycomb,color=signal,solid,line width=1pt}}
\pgfplotsset{signalhighlight/.style={ycomb,color=signal,solid,line width=1pt,mark=o,mark size=2pt}}

>>>>

% http://tex.stackexchange.com/questions/287975/pgfplots-layer-issue
\pgfplotsset{
/pgfplots/layers/mylayer/.define layer set=
{axis background,axis grid,main,axis ticks,axis lines,axis tick labels,axis descriptions,axis foreground}
{/pgfplots/layers/standard}
}
\pgfplotsset{/dummy/workaround/.style={/pgfplots/axis on top}}

\pgfplotsset{tick style={black!30},grid style={black!10}}
\pgfplotsset{every axis legend/.append style={font=\footnotesize}}
\pgfplotsset{every axis label/.append style={font=\footnotesize}}
\pgfplotsset{every tick label/.append style={font=\footnotesize}}
\pgfplotsset{every axis title/.append style={at={(0.5,1.025)}}}
\pgfplotsset{every axis/.append style={set layers=mylayer, /dummy/workaround}}
\pgfplotsset{every axis post/.style={unbounded coords=jump, line join=round}}

@@

\pgfplotsset{frf/.style={color=black,solid,line width=1pt}}
\pgfplotsset{bw/.style={fill=bwfill,draw=bwline,opacity=0.75,area legend}}
\pgfplotsset{signal/.style={ycomb,color=signal,solid,line width=1pt}}
\pgfplotsset{signalhighlight/.style={ycomb,color=signal,solid,line width=1pt,mark=o,mark size=2pt}}
